%-------------------------
% Resume in Latex
% Author : Indu dwivedi
% Adapted from: Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}

\usepackage[charter]{mathdesign} % Bitstream Charter
% \usepackage{newpxtext,newpxmath} % Palatino

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{2pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-1pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \small \textbf{\huge Venu Vardhan Reddy Tekula}} \\ 
  {(+91) 8186866445} | \href{mailto:venuvardhanreddytekula8@gmail.com}{venuvardhanreddytekula8@gmail.com} | \href{https://vchrombie.github.io}{vchrombie.github.io} \\
\href{https://github.com/vchrombie}{github.com/vchrombie} | \href{https://www.linkedin.com/in/tvvr/}{linkedin.com/in/tvvr/} | \href{https://twitter.com/vchrombie}{twitter.com/vchrombie}
 
\end{center}


%-----------SUMMARY-----------------
\shorterSection{Summary}
\small A proactive and fast learning individual seeking an opportunity to work as a dynamic data analyst utilizing analytical & methodical skills and relevant expertise to help the company achieve business goals while sticking to vision, mission and values.
\vspace{3pt}

%-----------EDUCATION-----------------
\shorterSection{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Amrita School of Engineering, Amrita Vishwa Vidyapeetham}{Amritapuri, Kollam, India.}
      {Bachelors of Technology in Computer Science;  GPA: 8.36/10.0}{Expected May 2020}
      \vspace{-5pt}
      {
          \resumeItemNoBullet{Areas of Interest}{Data Analytics, Data Science, Cyber Security Application with Machine Learning.}
          \resumeItemNoBullet{Relevant Coursework}{Scientific Computing, Database Management Systems, R for Data Science, Natural Language Processing.}
    }
    
%    \resumeSubheading
%		{Narayana Junior Collge}{Dilsukhnagar, Hyderabad, India}
%		{Higher Secondary;  Marks: 95\%}{Aug 2014 - May 2016}
      
  \resumeSubHeadingListEnd
  \vspace{3pt}

%-----------ACADEMIC PROJECTS AND INTERNSHIPS-----------------
\shorterSection{Projects}
  \resumeSubHeadingListStart
      
    \resumeSubItem{Star Wars Analysis}{It was a part of the \textit{Data Analytics} certification. I made a detailed analysis of the star-wars dataset using pandas and implemented the visualizations strategies using matplotlib. I made a few conclusions of the analysis too. I used Jupyter Notebooks for this project.}    
    
    \resumeSubItem{Airavat}{This project was made as a part of the \textit{Software Engineering} course considering the principles of \textit{Agile Development}. Developed, modified and implemented a train booking app which gives optimised results of any travel if you didn't get a ticket. Built using Flask and IRCTC API.}

    \resumeSubItem{GitLit}{It is a social networking site exclusively for OSS developers. Built with Django, GitHub GraphQL, Bootstrap and Saas.
        \vspace{-8pt}
        \begin{itemize}
            \item It works by connecting enthusiastic developers to the most interesting and relevant projects to them and forming new communities of like-minded and passionate developers.
			\vspace{-4pt}
            \item It works by generating suggestions to user, based on the scores of user and repository calculated based on a set of predefined metrics, through Collaborative Filtering. 
        \end{itemize}
      }
	
    \resumeSubItem{Malicious Web Content Detection using Machine Learning}{This is made as a part of the course \textit{Scientific Computing} under \textit{Dr. Sajeev G. P}, Dept. of CSE. A Chrome Extension which checks the website you are browsing, and categorize into SAFE/MALICIOUS, using Machine Learning. Built using Python, PHP, HTML/CSS.}
      
        \resumeSubItem{Amma Teachings}{An \textit{Amazon Alexa application} which gives you quotes given by \textit{Amma} whenever you trigger it with a voice call. Built with using Alexa Skill Kit, Python and AWS Lambda. The \textit{application got published in the Amazon Indian Store} too. \url{https://amzn.to/2TTlvD6}}
      
    \resumeSubItem{EcoTourism@Lambasingi}{{Student Social Responsibility Project}. We organized a 4-day campaign to \textit{promote cleanliness} in a \textit{remote place Lambasingi}, which is one of the villages in Andhra Pradesh near Visakhapatnam as a part of the \textit{SSR Project}.}    
    
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\shorterSection{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CHAOSS - The Linux Foundation}{}
      {Open Source Contributor}{January 2018 - Present}
      \resumeItemListStart
      \vspace{-2pt}
      	\item \small It is an Open Source project focused on creating analytics and metrics to help and define community health. 
        \vspace{-2pt}
        \item \small{We define, create and implement metrics which helps to make tools for the analysis of different Open Source communities. I am a part of two working groups.
        \vspace{-2pt}
        	\begin{itemize}
             	\resumeItem{WG-Evolution}{This working group is focused on the lifecycle of open source projects. Growth, Maturity and Decline are the important concepts of the metrics.}
       			\resumeItem{WG-Value}{This working group is focused on metrics for Economic Value in open source.}
         	\end{itemize}
        }
      \resumeItemListEnd

    \resumeSubheading
      {FOSS@Amrita}{Amritapuri, India}
      {Member and Student Mentor}{July 2016 - Present}
      \resumeItemListStart
        \item \small FOSS club trains students encourages contributions to free and open source soft-ware and skill development. I actively mentor juniors and participate in various clubactivities. I am the head of the Data Science Team.
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\shorterSection{Skills}
  \resumeSubHeadingListStart
  \small
    \item{
     \textbf{Languages}{: Python, C++, C, Java, SQL}}
	 \vspace{-5pt}
     \item{
     \textbf{Tools & Technologies}{: AWS, Git, GitHub, Docker, Jupyter Notebooks, Anaconda, MS Excel.}
    }
    \vspace{-5pt}
    \item{
     \textbf{Libraries}{: TensorFlow, Keras, Scikit-Learn, Numpy, Pandas, Spark, Jupyter.}
    }
\resumeSubHeadingListEnd




%-----------Addtional Experience & Achievements-----------------
\shorterSection{Additional Experience \& Achievements}
  \resumeSubHeadingListStart
  \small
    \item{Got selected as a student to the Data Mining Summer Program at Ben-Gurion University of the Negev (BGU), Israel with 92\% scholarship.}
    \vspace{-5pt}
    \item{I served as the \textbf{Head Coordinator} of the \textbf{Social Media Team} of the FOSS@Amrita club. }It manages the Social Media accounts of the club and keep update the students with the latest technologies.}
    \vspace{-5pt}
    \item{I served as the \textbf{Chief Coordinator} for the \textbf{dev-workshop} conducted by FOSS@Amrita which is training program for freshmen on various topics like Linux, Problem Solving, Automation using python and Web Development.}
    \vspace{-5pt}    
	\item{I served as the \textbf{Student Coordinator} for the \textbf{Venue Maintainence Seva} during \textbf{Amritavarsham} which is the birthday celebration of Mata Amritanandamayi Devi, popularly known as "\textbf{Amma}".}
    \vspace{-5pt}
    \item{I served as the \textbf{Student Coordinator} for the \textbf{Amala Bharatham Campaign (ABC)} conducted by \textbf{Mata Amritanandamayi Math} which aimed at cleaning India\textsc{\char10}s public places, national highways and tourist places.}
    \vspace{-5pt}
	\item{I was one of the \textbf{top 5 contributors} in \textbf{Kharagpur Winter of Code 2017 }which is conducted by the the Kharagpur Open Source Society of IIT Kharagpur.}
    \vspace{-5pt}

  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}